---
title: "<b> EATMINT1 - Sharing emotions contributes to regulating collaborative intentions in group problem-solving<b>"
subtitle: "<b>Descriptive statistics </b>"
author: "Sunny Avry"
date: "March 28th, 2019"
output:
  html_document:
    df_print: paged
    toc: true
  html_notebook: default
  pdf_document: default
  
---

<style type="text/css">

h1.title {
  font-size: 30px;
}
</style>

```{r message=FALSE, warning=FALSE}
library(xlsx);library(dplyr);library(lubridate)
```

```{r}
options(scipen=999) #remove scientific notation
data <- read.csv2("taux_utilisation_actes.csv")
data_eat <- data[data$eat == "Oui",]
data_eat
data_collaboration_duration <- read.csv2("timing_collaboration.csv")
data_collaboration_duration
```

## Global variables
```{r}
#window size
max.window.size <- 5 #size of the window = number of collaborative acts per window
max.window.size

#dyad having used the emotion awareness tool (eat condition) for sharing their emotions 
dyads_eat <- c(
"D02",
"D05",
"D07",
"D09",
"D13",
"D16",
"D21",
"D23",
"D26",
"D27",
"D29")

#participants in eat condition
participants_eat <- c(
"D02P01",
"D02P02",
"D05P01",
"D05P02",
"D07P01",
"D07P02",
"D09P01",
"D09P02",
"D13P01",
"D13P02",
"D16P01",
"D16P02",
"D21P01",
"D21P02",
"D23P01",
"D23P02",
"D26P01",
"D26P02",
"D27P01",
"D27P02",
"D29P01",
"D29P02")

#participants in no-eat condition
participants_no_eat <- c(
"D04P01",
"D04P02",
"D06P01",
"D06P02",
"D08P01",
"D08P02",
"D10P01",
"D10P02",
"D12P01",
"D12P02",
"D15P01",
"D15P02",
"D20P01",
"D20P02",
"D24P01",
"D24P02")

#emotions displayed during the collaborative problem-solving

emotions <- c(
"interested",
"focused",
"delighted",
"satisfied",
"confident",
"amused",
"relieved",
"relaxed",
"confused",
"stressed",
"dissatisfied",
"annoyed",
"frustrated",
"grateful",
"disappointed",
"empathic",
"bored",
"surprised",
"puzzled",
"anxious",
"impatient")

#All collaborative acts emitted by participants

collaborative.processes <- c(
"accept",
"agree",
"check.comprehension",
"check.reception",
"coordinate.teamwork",
"disagree",
"elicit.opinion",
"elicit.partner.information",
"elicit.proposition",
"elicit.recall",
"elicit.task.information",
"give.explanation",
"give.opinion.against",
"give.opinion.for",
"give.proposition",
"give.recall",
"give.self.information",
"give.task.information",
"incorporate",
"manage.task",
"other",
"outside.activity",
"relax.atmosphere",
"show.active.listening",
"show.reflection",
"show.hostility",
"show.solidarity",
"tool.discourse",
"use.social.convention")
```

# Emotions

## Total number of emotions
```{r}
overall.emotions.occurences <-  sum(data$shared.emotion != "") 
paste("total number of emotions =",overall.emotions.occurences)
```

## Number of occurences of the different emotions
```{r}

emotions.occurences.per.category <- c()
for (emotion in emotions){
  emotions.occurences.per.category[emotion] <- sum(data$shared.emotion == emotion)
}
emotions.occurences.per.category.sorted <- sort(emotions.occurences.per.category, decreasing = TRUE)
print("number of emotion per category: ")
emotions.occurences.per.category.sorted
```


## Number of emotions per participant
```{r}

emotions.occurences.per.participant <- c()
for (participant in participants_eat){
  emotions.occurences.per.participant[participant] <- sum(data$participant == participant & data$shared.emotion != "")
}
emotions.occurences.per.participant.sorted <- sort(emotions.occurences.per.participant, decreasing = TRUE)
print("number of emotion per participant: ")
emotions.occurences.per.participant.sorted
```

## Difference in the number of shared emotions in a same dyad

```{r}

d2 <- abs(emotions.occurences.per.participant.sorted[c("D02P01")]-emotions.occurences.per.participant.sorted[c("D02P02")])
d5 <- abs(emotions.occurences.per.participant.sorted[c("D05P01")]-emotions.occurences.per.participant.sorted[c("D05P02")])
d7 <- abs(emotions.occurences.per.participant.sorted[c("D07P01")]-emotions.occurences.per.participant.sorted[c("D07P02")])
d9 <- abs(emotions.occurences.per.participant.sorted[c("D09P01")]-emotions.occurences.per.participant.sorted[c("D09P02")])
d13 <- abs(emotions.occurences.per.participant.sorted[c("D13P01")]-emotions.occurences.per.participant.sorted[c("D13P02")])
d16 <- abs(emotions.occurences.per.participant.sorted[c("D16P01")]-emotions.occurences.per.participant.sorted[c("D16P02")])
d21 <- abs(emotions.occurences.per.participant.sorted[c("D21P01")]-emotions.occurences.per.participant.sorted[c("D21P02")])
d23 <- abs(emotions.occurences.per.participant.sorted[c("D23P01")]-emotions.occurences.per.participant.sorted[c("D23P02")])     
d26 <- abs(emotions.occurences.per.participant.sorted[c("D26P01")]-emotions.occurences.per.participant.sorted[c("D26P02")])
d27 <- abs(emotions.occurences.per.participant.sorted[c("D27P01")]-emotions.occurences.per.participant.sorted[c("D27P02")])  
d29 <- abs(emotions.occurences.per.participant.sorted[c("D29P01")]-emotions.occurences.per.participant.sorted[c("D29P02")])   


emotions.differences.per.dyad <- c(d2,d5,d7,d9,d13,d16,d21,d23,d26,d27,d29)
emotions.differences.per.dyad
print("mean: ")
mean(emotions.differences.per.dyad)
print("sd: ")
sd(emotions.differences.per.dyad)
```

## Frequency of the emotional sharing

```{r}

#"number of emotion per dyad: "
#D09 D26 D21 D13 D16 D29 D27 D07 D02 D23 D05 
#45  33  31  30  22  21  20  18  16  14  13 


#D02
len <- length(data_eat[data_eat$dyad == "D02",c("unix.time.video")])
d02 <- (data_eat[data_eat$dyad == "D02",c("unix.time.video")][len] - data_eat[data_eat$dyad == "D02",c("unix.time.video")][1]) / 16
seconds_to_period(d02)

#D05
len <- length(data_eat[data_eat$dyad == "D05",c("unix.time.video")])
d05 <- (data_eat[data_eat$dyad == "D05",c("unix.time.video")][len] - data_eat[data_eat$dyad == "D05",c("unix.time.video")][1]) / 13
seconds_to_period(d05)

#D07
len <- length(data_eat[data_eat$dyad == "D07",c("unix.time.video")])
d07 <- (data_eat[data_eat$dyad == "D07",c("unix.time.video")][len] - data_eat[data_eat$dyad == "D07",c("unix.time.video")][1]) / 18
seconds_to_period(d07)

#D09
len <- length(data_eat[data_eat$dyad == "D09",c("unix.time.video")])
d09 <- (data_eat[data_eat$dyad == "D09",c("unix.time.video")][len] - data_eat[data_eat$dyad == "D09",c("unix.time.video")][1]) / 45
seconds_to_period(d09)

#D13
len <- length(data_eat[data_eat$dyad == "D13",c("unix.time.video")])
d13 <- (data_eat[data_eat$dyad == "D13",c("unix.time.video")][len] - data_eat[data_eat$dyad == "D13",c("unix.time.video")][1]) / 30
seconds_to_period(d13)

#D16
len <- length(data_eat[data_eat$dyad == "D16",c("unix.time.video")])
d16 <- (data_eat[data_eat$dyad == "D16",c("unix.time.video")][len] - data_eat[data_eat$dyad == "D16",c("unix.time.video")][1]) / 22
seconds_to_period(d16)

#D21
len <- length(data_eat[data_eat$dyad == "D21",c("unix.time.video")])
d21 <- (data_eat[data_eat$dyad == "D21",c("unix.time.video")][len] - data_eat[data_eat$dyad == "D21",c("unix.time.video")][1]) / 31
seconds_to_period(d21)

#D23
len <- length(data_eat[data_eat$dyad == "D23",c("unix.time.video")])
d23 <- (data_eat[data_eat$dyad == "D23",c("unix.time.video")][len] - data_eat[data_eat$dyad == "D23",c("unix.time.video")][1]) / 14
seconds_to_period(d23)

#D26
len <- length(data_eat[data_eat$dyad == "D26",c("unix.time.video")])
d26 <- (data_eat[data_eat$dyad == "D26",c("unix.time.video")][len] - data_eat[data_eat$dyad == "D26",c("unix.time.video")][1]) / 22
seconds_to_period(d26)

#D27
len <- length(data_eat[data_eat$dyad == "D27",c("unix.time.video")])
d27 <- (data_eat[data_eat$dyad == "D27",c("unix.time.video")][len] - data_eat[data_eat$dyad == "D27",c("unix.time.video")][1]) / 20
seconds_to_period(d27)

#D29
len <- length(data_eat[data_eat$dyad == "D29",c("unix.time.video")])
d29 <- (data_eat[data_eat$dyad == "D29",c("unix.time.video")][len] - data_eat[data_eat$dyad == "D29",c("unix.time.video")][1]) / 21
seconds_to_period(d29)


time.sharing.emotions <- c(d02,d05,d07,d09,d13,d16,d21,d23,d26,d27,d29)
print("mean: ")
seconds_to_period(mean(time.sharing.emotions))
print("sd: ")
seconds_to_period(sd(time.sharing.emotions))

```

## Number of emotions per dyad

```{r}
emotions.occurences.per.dyad <- c()

for (dyad in dyads_eat){
  emotions.occurences.per.dyad[dyad] <- sum(data$dyad == dyad & data$shared.emotion != "")
}
emotions.occurences.per.dyad.sorted <- sort(emotions.occurences.per.dyad, decreasing = TRUE)
sum(emotions.occurences.per.dyad.sorted <- sort(emotions.occurences.per.dyad, decreasing = TRUE))
print("number of emotion per dyad: ")
emotions.occurences.per.dyad.sorted
print("mean: ")
mean(emotions.occurences.per.dyad.sorted)
print("standard deviation: ")
sd(emotions.occurences.per.dyad.sorted)
```

## Number of emotions per category per participant
```{r}
emotions.occurences.per.category.per.participant <- data.frame(row.names = participants_eat)

x <- c()
for (i in emotions) {
  for(j in participants_eat) {
   x[j] <- c(sum(data$shared.emotion == i & data$participant == j))
  }
  emotions.occurences.per.category.per.participant[i] <- x
}
emotions.occurences.per.category.per.participant
```

## Averaged number of each emotion
```{r}

averaged.number.of.each.emotion <- c()
for (i in emotions) {
  averaged.number.of.each.emotion[i] <- mean(emotions.occurences.per.category.per.participant[,i][emotions.occurences.per.category.per.participant[,i] != 0])
  }
averaged.number.of.each.emotion.sorted <- sort(averaged.number.of.each.emotion, decreasing = TRUE)
averaged.number.of.each.emotion.sorted
```


## Number of participants with at least one emotion for each emotion
```{r}
participants_eat.per.emotion <- c("interested" = sum((emotions.occurences.per.category.per.participant$interested != 0) == TRUE),
                             "focused" = sum((emotions.occurences.per.category.per.participant$focused != 0) == TRUE),
                             "delighted" = sum((emotions.occurences.per.category.per.participant$delighted != 0) == TRUE),
                             "satisfied" = sum((emotions.occurences.per.category.per.participant$satisfied != 0) == TRUE),
                             "confident" = sum((emotions.occurences.per.category.per.participant$confident != 0) == TRUE),
                             "amused" = sum((emotions.occurences.per.category.per.participant$amused != 0) == TRUE),
                             "relieved" = sum((emotions.occurences.per.category.per.participant$relieved != 0) == TRUE),
                             "relaxed" = sum((emotions.occurences.per.category.per.participant$relaxed != 0) == TRUE),
                             "confused" = sum((emotions.occurences.per.category.per.participant$confused != 0) == TRUE),
                             "stressed" = sum((emotions.occurences.per.category.per.participant$stressed != 0) == TRUE),
                             "dissatisfied" = sum((emotions.occurences.per.category.per.participant$dissatisfied != 0) == TRUE),
                             "annoyed" = sum((emotions.occurences.per.category.per.participant$annoyed != 0) == TRUE),
                             "frustrated" = sum((emotions.occurences.per.category.per.participant$frustrated != 0) == TRUE),
                             "grateful" = sum((emotions.occurences.per.category.per.participant$grateful != 0) == TRUE),
                             "disappointed" = sum((emotions.occurences.per.category.per.participant$disappointed != 0) == TRUE),
                             "empathic" = sum((emotions.occurences.per.category.per.participant$empathic != 0) == TRUE),
                             "bored" = sum((emotions.occurences.per.category.per.participant$bored != 0) == TRUE),
                             "surprised" = sum((emotions.occurences.per.category.per.participant$surprised != 0) == TRUE),
                             "puzzled" = sum((emotions.occurences.per.category.per.participant$puzzled != 0) == TRUE),
                             "anxious" = sum((emotions.occurences.per.category.per.participant$anxious != 0) == TRUE),
                             "impatient" = sum((emotions.occurences.per.category.per.participant$impatient != 0) == TRUE))
participants_eat.per.emotion.sorted <- sort(participants_eat.per.emotion, decreasing = TRUE)
participants_eat.per.emotion.sorted
```

# Number of positive and negative emotions per dyad

```{r}

negative.emotions.occurences.per.dyad <- c()

for (dyad in dyads_eat){
  negative.emotions.occurences.per.dyad[dyad] <- sum(data$dyad == dyad 
                                                     & (data$shared.emotion == "confused"
                                                     | data$shared.emotion == "frustrated"
                                                     | data$shared.emotion == "anxious"
                                                     | data$shared.emotion == "stressed"
                                                     | data$shared.emotion == "dissatisfied"
                                                     | data$shared.emotion == "annoyed"
                                                     | data$shared.emotion == "disappointed"
                                                     | data$shared.emotion == "bored"
                                                     | data$shared.emotion == "puzzled"
                                                     | data$shared.emotion == "impatient"))
}
negative.emotions.occurences.per.dyad
sum(negative.emotions.occurences.per.dyad)

positive.emotions.occurences.per.dyad <- c()

for (dyad in dyads_eat){
  positive.emotions.occurences.per.dyad[dyad] <- sum(data$dyad == dyad 
                                                     & (data$shared.emotion == "focused"
                                                     | data$shared.emotion == "interested"
                                                     | data$shared.emotion == "confident"
                                                     | data$shared.emotion == "satisfied"
                                                     | data$shared.emotion == "amused"
                                                     | data$shared.emotion == "delighted"
                                                     | data$shared.emotion == "relaxed"
                                                     | data$shared.emotion == "relieved"
                                                     | data$shared.emotion == "empathic"
                                                     | data$shared.emotion == "grateful"
                                                     | data$shared.emotion == "surprised"))
}
positive.emotions.occurences.per.dyad
sum(positive.emotions.occurences.per.dyad)
```

# Number of positive and negative emotions per participant

```{r}

negative.emotions.occurences.per.participant <- c()

for (participant in participants_eat){
  negative.emotions.occurences.per.participant[participant] <- sum(data$participant == participant 
                                                     & (data$shared.emotion == "confused"
                                                     | data$shared.emotion == "frustrated"
                                                     | data$shared.emotion == "anxious"
                                                     | data$shared.emotion == "stressed"
                                                     | data$shared.emotion == "dissatisfied"
                                                     | data$shared.emotion == "annoyed"
                                                     | data$shared.emotion == "disappointed"
                                                     | data$shared.emotion == "bored"
                                                     | data$shared.emotion == "puzzled"
                                                     | data$shared.emotion == "impatient"))
}
negative.emotions.occurences.per.participant
sum(negative.emotions.occurences.per.participant)

positive.emotions.occurences.per.participant <- c()

for (participant in participants_eat){
  positive.emotions.occurences.per.participant[participant] <- sum(data$participant == participant 
                                                      & (data$shared.emotion == "focused"
                                                     | data$shared.emotion == "interested"
                                                     | data$shared.emotion == "confident"
                                                     | data$shared.emotion == "satisfied"
                                                     | data$shared.emotion == "amused"
                                                     | data$shared.emotion == "delighted"
                                                     | data$shared.emotion == "relaxed"
                                                     | data$shared.emotion == "relieved"
                                                     | data$shared.emotion == "empathic"
                                                     | data$shared.emotion == "grateful"
                                                     | data$shared.emotion == "surprised"))
}
positive.emotions.occurences.per.participant
sum(positive.emotions.occurences.per.participant)
```

# Collaborative acts


## Total time of collaboration

```{r}

collaboration_duration <- seconds_to_period(data_collaboration_duration$collaboration.duration/1000)
names(collaboration_duration) <- c("D02","D05", "D07", "D09", "D13","D16", "D21", "D23", "D26", "D27", "D29")

collaboration_duration

print("mean: ")
seconds_to_period(mean(data_collaboration_duration$collaboration.duration/1000))

print("sd: ")
seconds_to_period(sd(data_collaboration_duration$collaboration.duration/1000))
```


## Total number of collaborative acts
```{r}

overall.collaborative.processes.occurences <- length(which(data$eat == "Oui"))
overall.collaborative.processes.occurences
```
## Number of collaborative acts per participant
```{r}
collaborative.processes.occurences.per.participant <- c()
for (participant in participants_eat){
  collaborative.processes.occurences.per.participant[participant] <- sum(data$participant == participant)
}
collaborative.processes.occurences.per.participant.sorted <- sort(collaborative.processes.occurences.per.participant, decreasing = TRUE)
print("number of emotion per participant: ")
collaborative.processes.occurences.per.participant.sorted
```

## Number of collaborative acts per dyad
```{r}
collaborative.processes.occurences.per.dyad <- c()
for (dyad in dyads_eat){
  collaborative.processes.occurences.per.dyad[dyad] <- sum(data$dyad == dyad)
}
collaborative.processes.occurences.per.dyad.sorted <- sort(collaborative.processes.occurences.per.dyad, decreasing = TRUE)
print("number of emotion per dyad: ")
collaborative.processes.occurences.per.dyad.sorted
print("mean: ")
mean(collaborative.processes.occurences.per.dyad.sorted)
print("sd: ")
sd(collaborative.processes.occurences.per.dyad.sorted)
```



## Averaged number of collaborative acts
```{r}
mean(collaborative.processes.occurences.per.participant.sorted)
sd(collaborative.processes.occurences.per.participant.sorted)
```
## Number of collaborative acts per category
```{r}
collaborative.processes.occurences.per.category <- c()
for (i in collaborative.processes) {
   collaborative.processes.occurences.per.category[i] <- sum(data_eat$collaborative.processes == i)
  }
collaborative.processes.occurences.per.category
collaborative.processes.occurences.per.category.sorted <- sort(collaborative.processes.occurences.per.category, decreasing = TRUE)
collaborative.processes.occurences.per.category.sorted
sum(collaborative.processes.occurences.per.category.sorted)
```
## Averaged percentages of collaborative acts per category
```{r}
averaged.percentage.of.collaborative.processes.per.category <- sort(collaborative.processes.occurences.per.category/5141, decreasing = TRUE)
averaged.percentage.of.collaborative.processes.per.category
```
## Duration of collaborative acts per dyad
```{r}
average.time.collaboration.per.dyad <- c()
for (i in dyads_eat) {
   average.time.collaboration.per.dyad[i] <- sum(data$duration[data$dyad == i])
  }
average.time.collaboration.per.dyad
sum(data_eat$duration) / 5141
mean(data_eat$duration)
sd(data_eat$duration)
sum(average.time.collaboration.per.dyad) / 5141

seconds_to_period(mean(average.time.collaboration.per.dyad))
seconds_to_period(sd(average.time.collaboration.per.dyad))
```
## Number of collaborative acts per category per participant
```{r}
collaborative.processes.occurences.per.category.per.participant <- data.frame(row.names = participants_eat)
collaborative.processes.occurences.per.category.per.participant.percentage <- data.frame(row.names = participants_eat)

x <- c()
for (i in collaborative.processes) {
  for(j in participants_eat) {
   x[j] <- c(sum(data$collaborative.processes == i & data$participant == j))
  }
  collaborative.processes.occurences.per.category.per.participant[i] <- x
}
collaborative.processes.occurences.per.category.per.participant

x <- c()
for (i in collaborative.processes) {
  for(j in participants_eat) {
   x[j] <- c(sum(data$collaborative.processes == i & data$participant == j)/sum(data$participant == j))
  }
  collaborative.processes.occurences.per.category.per.participant.percentage[i] <- x
}
collaborative.processes.occurences.per.category.per.participant.percentage
```



