---
title: "<b> EATMINT1 - Sharing emotions contributes to regulating collaborative intentions in group problem-solving<br></b>"
subtitle: "<b>Emotion per collaborative phases </b>"
author: "Sunny Avry"
date: "April 2nd, 2020"
output:
  html_document:
    toc: true
    df_print: paged
  html_notebook: default
  pdf_document: default
  
---

<style type="text/css">

h1.title {
  font-size: 30px;
}
</style>

## Libraries
```{r message=FALSE, warning=FALSE}
library(xlsx);library(dplyr);library(lubridate)
```

```{r}
options(scipen=999) #remove scientific notation
data <- read.csv2("taux_utilisation_actes.csv")
data_eat <- data[data$eat == "Oui",]
data_eat
```

## Global variables
```{r}
#window size
max.window.size <- 5 #size of the window = number of collaborative acts per window
max.window.size

#dyad having used the emotion awareness tool (eat condition) for sharing their emotions 
dyads_eat <- c(
"D02",
"D05",
"D07",
"D09",
"D13",
"D16",
"D21",
"D23",
"D26",
"D27",
"D29")

#participants in eat condition
participants_eat <- c(
"D02P01",
"D02P02",
"D05P01",
"D05P02",
"D07P01",
"D07P02",
"D09P01",
"D09P02",
"D13P01",
"D13P02",
"D16P01",
"D16P02",
"D21P01",
"D21P02",
"D23P01",
"D23P02",
"D26P01",
"D26P02",
"D27P01",
"D27P02",
"D29P01",
"D29P02")

#participants in no-eat condition
participants_no_eat <- c(
"D04P01",
"D04P02",
"D06P01",
"D06P02",
"D08P01",
"D08P02",
"D10P01",
"D10P02",
"D12P01",
"D12P02",
"D15P01",
"D15P02",
"D20P01",
"D20P02",
"D24P01",
"D24P02")

# #emotions displayed during the collaborative problem-solving
# emotions <- c(
# "interested",
# "focused",
# "delighted",
# "satisfied",
# "confident",
# "amused",
# "relieved",
# "relaxed",
# "confused",
# "stressed",
# "dissatisfied",
# "annoyed",
# "frustrated",
# "grateful",
# "disappointed",
# "empathic",
# "bored",
# "surprised",
# "puzzled",
# "anxious",
# "impatient")

#All collaborative acts emitted by participants

# collaborative.processes <- c(
# "accept",
# "agree",
# "check.comprehension",
# "check.reception",
# "coordinate.teamwork",
# "disagree",
# "elicit.opinion",
# "elicit.partner.information",
# "elicit.proposition",
# "elicit.recall",
# "elicit.task.information",
# "give.explanation",
# "give.opinion.against",
# "give.opinion.for",
# "give.proposition",
# "give.recall",
# "give.self.information",
# "give.task.information",
# "incorporate",
# "manage.task",
# "other",
# "outside.activity",
# "relax.atmosphere",
# "show.active.listening",
# "show.reflection",
# "show.hostility",
# "show.solidarity",
# "tool.discourse",
# "use.social.convention")
```

```{r}
#All collaborative acts emitted by participants representing at least 4 percents of the total

collaborative.processes <- c(
"accept",
"agree",
"give.opinion.for",
"give.proposition",
"give.self.information",
"give.task.information",
"manage.task",
"relax.atmosphere",
"show.reflection",
"tool.discourse")


#emotions displayed during the collaborative problem-solving representating at least 
emotions <- c(
"interested",
"focused",
"delighted",
"satisfied",
"amused",
"relaxed")
```

Phase 1 represented 40% of the time
Phase 2 represented 40% of the time
Phase 3 represented 20% of the time


```{r}
n <- matrix(data=NA,nrow=3,ncol=0)
number.of.emotion.per.phase <- data.frame(n)
rownames(number.of.emotion.per.phase) <- c("phase1", "phase2","phase3")
number.of.emotion.per.phase
```

# d02

```{r}
d02 <- data_eat[data_eat$dyad == "D02",]

elapsed_time_d02 <- sum(d02$duration)
```

## interested
```{r}
phase1_end_time_d02 <- elapsed_time_d02 * (2/5)
phase2_end_time_d02 <- phase1_end_time_d02 * 2
phase3_end_time_d02 <- elapsed_time_d02

interested <- c(sum(d02[d02$elapsed.time <= phase1_end_time_d02,"shared.emotion"] == "interested"),
sum(d02[d02$elapsed.time > phase1_end_time_d02 & d02$elapsed.time <= phase2_end_time_d02 ,"shared.emotion"] == "interested"),
sum(d02[d02$elapsed.time > phase2_end_time_d02 & d02$elapsed.time <= phase3_end_time_d02,"shared.emotion"] == "interested"))

number.of.emotion.per.phase$interested <- interested
```

## focused
```{r}
phase1_end_time_d02 <- elapsed_time_d02 * (2/5)
phase2_end_time_d02 <- phase1_end_time_d02 * 2
phase3_end_time_d02 <- elapsed_time_d02

focused <- c(sum(d02[d02$elapsed.time <= phase1_end_time_d02,"shared.emotion"] == "focused"),
sum(d02[d02$elapsed.time > phase1_end_time_d02 & d02$elapsed.time <= phase2_end_time_d02 ,"shared.emotion"] == "focused"),
sum(d02[d02$elapsed.time > phase2_end_time_d02 & d02$elapsed.time <= phase3_end_time_d02,"shared.emotion"] == "focused"))

number.of.emotion.per.phase$focused <- focused
```

## delighted
```{r}
phase1_end_time_d02 <- elapsed_time_d02 * (2/5)
phase2_end_time_d02 <- phase1_end_time_d02 * 2
phase3_end_time_d02 <- elapsed_time_d02

delighted <- c(sum(d02[d02$elapsed.time <= phase1_end_time_d02,"shared.emotion"] == "delighted"),
sum(d02[d02$elapsed.time > phase1_end_time_d02 & d02$elapsed.time <= phase2_end_time_d02 ,"shared.emotion"] == "delighted"),
sum(d02[d02$elapsed.time > phase2_end_time_d02 & d02$elapsed.time <= phase3_end_time_d02,"shared.emotion"] == "delighted"))

number.of.emotion.per.phase$delighted <- delighted
```

## satisfied
```{r}
phase1_end_time_d02 <- elapsed_time_d02 * (2/5)
phase2_end_time_d02 <- phase1_end_time_d02 * 2
phase3_end_time_d02 <- elapsed_time_d02

satisfied <- c(sum(d02[d02$elapsed.time <= phase1_end_time_d02,"shared.emotion"] == "satisfied"),
sum(d02[d02$elapsed.time > phase1_end_time_d02 & d02$elapsed.time <= phase2_end_time_d02 ,"shared.emotion"] == "satisfied"),
sum(d02[d02$elapsed.time > phase2_end_time_d02 & d02$elapsed.time <= phase3_end_time_d02,"shared.emotion"] == "satisfied"))

number.of.emotion.per.phase$satisfied <- satisfied
```

## amused
```{r}
phase1_end_time_d02 <- elapsed_time_d02 * (2/5)
phase2_end_time_d02 <- phase1_end_time_d02 * 2
phase3_end_time_d02 <- elapsed_time_d02

amused <- c(sum(d02[d02$elapsed.time <= phase1_end_time_d02,"shared.emotion"] == "amused"),
sum(d02[d02$elapsed.time > phase1_end_time_d02 & d02$elapsed.time <= phase2_end_time_d02 ,"shared.emotion"] == "amused"),
sum(d02[d02$elapsed.time > phase2_end_time_d02 & d02$elapsed.time <= phase3_end_time_d02,"shared.emotion"] == "amused"))

number.of.emotion.per.phase$amused <- amused
```

## relaxed
```{r}
phase1_end_time_d02 <- elapsed_time_d02 * (2/5)
phase2_end_time_d02 <- phase1_end_time_d02 * 2
phase3_end_time_d02 <- elapsed_time_d02

relaxed <- c(sum(d02[d02$elapsed.time <= phase1_end_time_d02,"shared.emotion"] == "relaxed"),
sum(d02[d02$elapsed.time > phase1_end_time_d02 & d02$elapsed.time <= phase2_end_time_d02 ,"shared.emotion"] == "relaxed"),
sum(d02[d02$elapsed.time > phase2_end_time_d02 & d02$elapsed.time <= phase3_end_time_d02,"shared.emotion"] == "relaxed"))

number.of.emotion.per.phase$relaxed <- relaxed
```

# d05

```{r}
d05 <- data_eat[data_eat$dyad == "D05",]

elapsed_time_d05 <- sum(d05$duration)
```


## interested
```{r}
phase1_end_time_d05 <- elapsed_time_d05 * (2/5)
phase2_end_time_d05 <- phase1_end_time_d05 * 2
phase3_end_time_d05 <- elapsed_time_d05

interested <- c(sum(d05[d05$elapsed.time <= phase1_end_time_d05,"shared.emotion"] == "interested"),
sum(d05[d05$elapsed.time > phase1_end_time_d05 & d05$elapsed.time <= phase2_end_time_d05 ,"shared.emotion"] == "interested"),
sum(d05[d05$elapsed.time > phase2_end_time_d05 & d05$elapsed.time <= phase3_end_time_d05,"shared.emotion"] == "interested"))

number.of.emotion.per.phase$interested <- number.of.emotion.per.phase$interested + interested
```

## focused
```{r}
phase1_end_time_d05 <- elapsed_time_d05 * (2/5)
phase2_end_time_d05 <- phase1_end_time_d05 * 2
phase3_end_time_d05 <- elapsed_time_d05

focused <- c(sum(d05[d05$elapsed.time <= phase1_end_time_d05,"shared.emotion"] == "focused"),
sum(d05[d05$elapsed.time > phase1_end_time_d05 & d05$elapsed.time <= phase2_end_time_d05 ,"shared.emotion"] == "focused"),
sum(d05[d05$elapsed.time > phase2_end_time_d05 & d05$elapsed.time <= phase3_end_time_d05,"shared.emotion"] == "focused"))

number.of.emotion.per.phase$focused <- number.of.emotion.per.phase$focused + focused 
```

## delighted
```{r}
phase1_end_time_d05 <- elapsed_time_d05 * (2/5)
phase2_end_time_d05 <- phase1_end_time_d05 * 2
phase3_end_time_d05 <- elapsed_time_d05

delighted <- c(sum(d05[d05$elapsed.time <= phase1_end_time_d05,"shared.emotion"] == "delighted"),
sum(d05[d05$elapsed.time > phase1_end_time_d05 & d05$elapsed.time <= phase2_end_time_d05 ,"shared.emotion"] == "delighted"),
sum(d05[d05$elapsed.time > phase2_end_time_d05 & d05$elapsed.time <= phase3_end_time_d05,"shared.emotion"] == "delighted"))

number.of.emotion.per.phase$delighted <- number.of.emotion.per.phase$delighted + delighted 
```

## satisfied
```{r}
phase1_end_time_d05 <- elapsed_time_d05 * (2/5)
phase2_end_time_d05 <- phase1_end_time_d05 * 2
phase3_end_time_d05 <- elapsed_time_d05

satisfied <- c(sum(d05[d05$elapsed.time <= phase1_end_time_d05,"shared.emotion"] == "satisfied"),
sum(d05[d05$elapsed.time > phase1_end_time_d05 & d05$elapsed.time <= phase2_end_time_d05 ,"shared.emotion"] == "satisfied"),
sum(d05[d05$elapsed.time > phase2_end_time_d05 & d05$elapsed.time <= phase3_end_time_d05,"shared.emotion"] == "satisfied"))

number.of.emotion.per.phase$satisfied <- number.of.emotion.per.phase$satisfied + satisfied 
```

## amused
```{r}
phase1_end_time_d05 <- elapsed_time_d05 * (2/5)
phase2_end_time_d05 <- phase1_end_time_d05 * 2
phase3_end_time_d05 <- elapsed_time_d05

amused <- c(sum(d05[d05$elapsed.time <= phase1_end_time_d05,"shared.emotion"] == "amused"),
sum(d05[d05$elapsed.time > phase1_end_time_d05 & d05$elapsed.time <= phase2_end_time_d05 ,"shared.emotion"] == "amused"),
sum(d05[d05$elapsed.time > phase2_end_time_d05 & d05$elapsed.time <= phase3_end_time_d05,"shared.emotion"] == "amused"))

number.of.emotion.per.phase$amused <- number.of.emotion.per.phase$amused + amused 
```

## relaxed
```{r}
phase1_end_time_d05 <- elapsed_time_d05 * (2/5)
phase2_end_time_d05 <- phase1_end_time_d05 * 2
phase3_end_time_d05 <- elapsed_time_d05

relaxed <- c(sum(d05[d05$elapsed.time <= phase1_end_time_d05,"shared.emotion"] == "relaxed"),
sum(d05[d05$elapsed.time > phase1_end_time_d05 & d05$elapsed.time <= phase2_end_time_d05 ,"shared.emotion"] == "relaxed"),
sum(d05[d05$elapsed.time > phase2_end_time_d05 & d05$elapsed.time <= phase3_end_time_d05,"shared.emotion"] == "relaxed"))

number.of.emotion.per.phase$relaxed <- number.of.emotion.per.phase$relaxed + relaxed 
```

# d07

```{r}
d07 <- data_eat[data_eat$dyad == "D07",]

elapsed_time_d07 <- sum(d07$duration)
```


## interested
```{r}
phase1_end_time_d07 <- elapsed_time_d07 * (2/5)
phase2_end_time_d07 <- phase1_end_time_d07 * 2
phase3_end_time_d07 <- elapsed_time_d07

interested <- c(sum(d07[d07$elapsed.time <= phase1_end_time_d07,"shared.emotion"] == "interested"),
sum(d07[d07$elapsed.time > phase1_end_time_d07 & d07$elapsed.time <= phase2_end_time_d07 ,"shared.emotion"] == "interested"),
sum(d07[d07$elapsed.time > phase2_end_time_d07 & d07$elapsed.time <= phase3_end_time_d07,"shared.emotion"] == "interested"))

number.of.emotion.per.phase$interested <- number.of.emotion.per.phase$interested + interested
```

## focused
```{r}
phase1_end_time_d07 <- elapsed_time_d07 * (2/5)
phase2_end_time_d07 <- phase1_end_time_d07 * 2
phase3_end_time_d07 <- elapsed_time_d07

focused <- c(sum(d07[d07$elapsed.time <= phase1_end_time_d07,"shared.emotion"] == "focused"),
sum(d07[d07$elapsed.time > phase1_end_time_d07 & d07$elapsed.time <= phase2_end_time_d07 ,"shared.emotion"] == "focused"),
sum(d07[d07$elapsed.time > phase2_end_time_d07 & d07$elapsed.time <= phase3_end_time_d07,"shared.emotion"] == "focused"))

number.of.emotion.per.phase$focused <- number.of.emotion.per.phase$focused + focused 
```

## delighted
```{r}
phase1_end_time_d07 <- elapsed_time_d07 * (2/5)
phase2_end_time_d07 <- phase1_end_time_d07 * 2
phase3_end_time_d07 <- elapsed_time_d07

delighted <- c(sum(d07[d07$elapsed.time <= phase1_end_time_d07,"shared.emotion"] == "delighted"),
sum(d07[d07$elapsed.time > phase1_end_time_d07 & d07$elapsed.time <= phase2_end_time_d07 ,"shared.emotion"] == "delighted"),
sum(d07[d07$elapsed.time > phase2_end_time_d07 & d07$elapsed.time <= phase3_end_time_d07,"shared.emotion"] == "delighted"))

number.of.emotion.per.phase$delighted <- number.of.emotion.per.phase$delighted + delighted 
```

## satisfied
```{r}
phase1_end_time_d07 <- elapsed_time_d07 * (2/5)
phase2_end_time_d07 <- phase1_end_time_d07 * 2
phase3_end_time_d07 <- elapsed_time_d07

satisfied <- c(sum(d07[d07$elapsed.time <= phase1_end_time_d07,"shared.emotion"] == "satisfied"),
sum(d07[d07$elapsed.time > phase1_end_time_d07 & d07$elapsed.time <= phase2_end_time_d07 ,"shared.emotion"] == "satisfied"),
sum(d07[d07$elapsed.time > phase2_end_time_d07 & d07$elapsed.time <= phase3_end_time_d07,"shared.emotion"] == "satisfied"))

number.of.emotion.per.phase$satisfied <- number.of.emotion.per.phase$satisfied + satisfied 
```

## amused
```{r}
phase1_end_time_d07 <- elapsed_time_d07 * (2/5)
phase2_end_time_d07 <- phase1_end_time_d07 * 2
phase3_end_time_d07 <- elapsed_time_d07

amused <- c(sum(d07[d07$elapsed.time <= phase1_end_time_d07,"shared.emotion"] == "amused"),
sum(d07[d07$elapsed.time > phase1_end_time_d07 & d07$elapsed.time <= phase2_end_time_d07 ,"shared.emotion"] == "amused"),
sum(d07[d07$elapsed.time > phase2_end_time_d07 & d07$elapsed.time <= phase3_end_time_d07,"shared.emotion"] == "amused"))

number.of.emotion.per.phase$amused <- number.of.emotion.per.phase$amused + amused 
```

## relaxed
```{r}
phase1_end_time_d07 <- elapsed_time_d07 * (2/5)
phase2_end_time_d07 <- phase1_end_time_d07 * 2
phase3_end_time_d07 <- elapsed_time_d07

relaxed <- c(sum(d07[d07$elapsed.time <= phase1_end_time_d07,"shared.emotion"] == "relaxed"),
sum(d07[d07$elapsed.time > phase1_end_time_d07 & d07$elapsed.time <= phase2_end_time_d07 ,"shared.emotion"] == "relaxed"),
sum(d07[d07$elapsed.time > phase2_end_time_d07 & d07$elapsed.time <= phase3_end_time_d07,"shared.emotion"] == "relaxed"))

number.of.emotion.per.phase$relaxed <- number.of.emotion.per.phase$relaxed + relaxed 
```

# d09

```{r}
d09 <- data_eat[data_eat$dyad == "D09",]

elapsed_time_d09 <- sum(d09$duration)
```


## interested
```{r}
phase1_end_time_d09 <- elapsed_time_d09 * (2/5)
phase2_end_time_d09 <- phase1_end_time_d09 * 2
phase3_end_time_d09 <- elapsed_time_d09

interested <- c(sum(d09[d09$elapsed.time <= phase1_end_time_d09,"shared.emotion"] == "interested"),
sum(d09[d09$elapsed.time > phase1_end_time_d09 & d09$elapsed.time <= phase2_end_time_d09 ,"shared.emotion"] == "interested"),
sum(d09[d09$elapsed.time > phase2_end_time_d09 & d09$elapsed.time <= phase3_end_time_d09,"shared.emotion"] == "interested"))

number.of.emotion.per.phase$interested <- number.of.emotion.per.phase$interested + interested
```

## focused
```{r}
phase1_end_time_d09 <- elapsed_time_d09 * (2/5)
phase2_end_time_d09 <- phase1_end_time_d09 * 2
phase3_end_time_d09 <- elapsed_time_d09

focused <- c(sum(d09[d09$elapsed.time <= phase1_end_time_d09,"shared.emotion"] == "focused"),
sum(d09[d09$elapsed.time > phase1_end_time_d09 & d09$elapsed.time <= phase2_end_time_d09 ,"shared.emotion"] == "focused"),
sum(d09[d09$elapsed.time > phase2_end_time_d09 & d09$elapsed.time <= phase3_end_time_d09,"shared.emotion"] == "focused"))

number.of.emotion.per.phase$focused <- number.of.emotion.per.phase$focused + focused 
```

## delighted
```{r}
phase1_end_time_d09 <- elapsed_time_d09 * (2/5)
phase2_end_time_d09 <- phase1_end_time_d09 * 2
phase3_end_time_d09 <- elapsed_time_d09

delighted <- c(sum(d09[d09$elapsed.time <= phase1_end_time_d09,"shared.emotion"] == "delighted"),
sum(d09[d09$elapsed.time > phase1_end_time_d09 & d09$elapsed.time <= phase2_end_time_d09 ,"shared.emotion"] == "delighted"),
sum(d09[d09$elapsed.time > phase2_end_time_d09 & d09$elapsed.time <= phase3_end_time_d09,"shared.emotion"] == "delighted"))

number.of.emotion.per.phase$delighted <- number.of.emotion.per.phase$delighted + delighted 
```

## satisfied
```{r}
phase1_end_time_d09 <- elapsed_time_d09 * (2/5)
phase2_end_time_d09 <- phase1_end_time_d09 * 2
phase3_end_time_d09 <- elapsed_time_d09

satisfied <- c(sum(d09[d09$elapsed.time <= phase1_end_time_d09,"shared.emotion"] == "satisfied"),
sum(d09[d09$elapsed.time > phase1_end_time_d09 & d09$elapsed.time <= phase2_end_time_d09 ,"shared.emotion"] == "satisfied"),
sum(d09[d09$elapsed.time > phase2_end_time_d09 & d09$elapsed.time <= phase3_end_time_d09,"shared.emotion"] == "satisfied"))

number.of.emotion.per.phase$satisfied <- number.of.emotion.per.phase$satisfied + satisfied 
```

## amused
```{r}
phase1_end_time_d09 <- elapsed_time_d09 * (2/5)
phase2_end_time_d09 <- phase1_end_time_d09 * 2
phase3_end_time_d09 <- elapsed_time_d09

amused <- c(sum(d09[d09$elapsed.time <= phase1_end_time_d09,"shared.emotion"] == "amused"),
sum(d09[d09$elapsed.time > phase1_end_time_d09 & d09$elapsed.time <= phase2_end_time_d09 ,"shared.emotion"] == "amused"),
sum(d09[d09$elapsed.time > phase2_end_time_d09 & d09$elapsed.time <= phase3_end_time_d09,"shared.emotion"] == "amused"))

number.of.emotion.per.phase$amused <- number.of.emotion.per.phase$amused + amused 
```

## relaxed
```{r}
phase1_end_time_d09 <- elapsed_time_d09 * (2/5)
phase2_end_time_d09 <- phase1_end_time_d09 * 2
phase3_end_time_d09 <- elapsed_time_d09

relaxed <- c(sum(d09[d09$elapsed.time <= phase1_end_time_d09,"shared.emotion"] == "relaxed"),
sum(d09[d09$elapsed.time > phase1_end_time_d09 & d09$elapsed.time <= phase2_end_time_d09 ,"shared.emotion"] == "relaxed"),
sum(d09[d09$elapsed.time > phase2_end_time_d09 & d09$elapsed.time <= phase3_end_time_d09,"shared.emotion"] == "relaxed"))

number.of.emotion.per.phase$relaxed <- number.of.emotion.per.phase$relaxed + relaxed 
```

# d13

```{r}
d13 <- data_eat[data_eat$dyad == "D13",]

elapsed_time_d13 <- sum(d13$duration)
```
## interested
```{r}
phase1_end_time_d13 <- elapsed_time_d13 * (2/5)
phase2_end_time_d13 <- phase1_end_time_d13 * 2
phase3_end_time_d13 <- elapsed_time_d13

interested <- c(sum(d13[d13$elapsed.time <= phase1_end_time_d13,"shared.emotion"] == "interested"),
sum(d13[d13$elapsed.time > phase1_end_time_d13 & d13$elapsed.time <= phase2_end_time_d13 ,"shared.emotion"] == "interested"),
sum(d13[d13$elapsed.time > phase2_end_time_d13 & d13$elapsed.time <= phase3_end_time_d13,"shared.emotion"] == "interested"))

number.of.emotion.per.phase$interested <- number.of.emotion.per.phase$interested + interested
```

## focused
```{r}
phase1_end_time_d13 <- elapsed_time_d13 * (2/5)
phase2_end_time_d13 <- phase1_end_time_d13 * 2
phase3_end_time_d13 <- elapsed_time_d13

focused <- c(sum(d13[d13$elapsed.time <= phase1_end_time_d13,"shared.emotion"] == "focused"),
sum(d13[d13$elapsed.time > phase1_end_time_d13 & d13$elapsed.time <= phase2_end_time_d13 ,"shared.emotion"] == "focused"),
sum(d13[d13$elapsed.time > phase2_end_time_d13 & d13$elapsed.time <= phase3_end_time_d13,"shared.emotion"] == "focused"))

number.of.emotion.per.phase$focused <- number.of.emotion.per.phase$focused + focused 
```

## delighted
```{r}
phase1_end_time_d13 <- elapsed_time_d13 * (2/5)
phase2_end_time_d13 <- phase1_end_time_d13 * 2
phase3_end_time_d13 <- elapsed_time_d13

delighted <- c(sum(d13[d13$elapsed.time <= phase1_end_time_d13,"shared.emotion"] == "delighted"),
sum(d13[d13$elapsed.time > phase1_end_time_d13 & d13$elapsed.time <= phase2_end_time_d13 ,"shared.emotion"] == "delighted"),
sum(d13[d13$elapsed.time > phase2_end_time_d13 & d13$elapsed.time <= phase3_end_time_d13,"shared.emotion"] == "delighted"))

number.of.emotion.per.phase$delighted <- number.of.emotion.per.phase$delighted + delighted 
```

## satisfied
```{r}
phase1_end_time_d13 <- elapsed_time_d13 * (2/5)
phase2_end_time_d13 <- phase1_end_time_d13 * 2
phase3_end_time_d13 <- elapsed_time_d13

satisfied <- c(sum(d13[d13$elapsed.time <= phase1_end_time_d13,"shared.emotion"] == "satisfied"),
sum(d13[d13$elapsed.time > phase1_end_time_d13 & d13$elapsed.time <= phase2_end_time_d13 ,"shared.emotion"] == "satisfied"),
sum(d13[d13$elapsed.time > phase2_end_time_d13 & d13$elapsed.time <= phase3_end_time_d13,"shared.emotion"] == "satisfied"))

number.of.emotion.per.phase$satisfied <- number.of.emotion.per.phase$satisfied + satisfied 
```

## amused
```{r}
phase1_end_time_d13 <- elapsed_time_d13 * (2/5)
phase2_end_time_d13 <- phase1_end_time_d13 * 2
phase3_end_time_d13 <- elapsed_time_d13

amused <- c(sum(d13[d13$elapsed.time <= phase1_end_time_d13,"shared.emotion"] == "amused"),
sum(d13[d13$elapsed.time > phase1_end_time_d13 & d13$elapsed.time <= phase2_end_time_d13 ,"shared.emotion"] == "amused"),
sum(d13[d13$elapsed.time > phase2_end_time_d13 & d13$elapsed.time <= phase3_end_time_d13,"shared.emotion"] == "amused"))

number.of.emotion.per.phase$amused <- number.of.emotion.per.phase$amused + amused 
```

## relaxed
```{r}
phase1_end_time_d13 <- elapsed_time_d13 * (2/5)
phase2_end_time_d13 <- phase1_end_time_d13 * 2
phase3_end_time_d13 <- elapsed_time_d13

relaxed <- c(sum(d13[d13$elapsed.time <= phase1_end_time_d13,"shared.emotion"] == "relaxed"),
sum(d13[d13$elapsed.time > phase1_end_time_d13 & d13$elapsed.time <= phase2_end_time_d13 ,"shared.emotion"] == "relaxed"),
sum(d13[d13$elapsed.time > phase2_end_time_d13 & d13$elapsed.time <= phase3_end_time_d13,"shared.emotion"] == "relaxed"))

number.of.emotion.per.phase$relaxed <- number.of.emotion.per.phase$relaxed + relaxed 
```

# d16

```{r}
d16 <- data_eat[data_eat$dyad == "D16",]

elapsed_time_d16 <- sum(d16$duration)
```
## interested
```{r}
phase1_end_time_d16 <- elapsed_time_d16 * (2/5)
phase2_end_time_d16 <- phase1_end_time_d16 * 2
phase3_end_time_d16 <- elapsed_time_d16

interested <- c(sum(d16[d16$elapsed.time <= phase1_end_time_d16,"shared.emotion"] == "interested"),
sum(d16[d16$elapsed.time > phase1_end_time_d16 & d16$elapsed.time <= phase2_end_time_d16 ,"shared.emotion"] == "interested"),
sum(d16[d16$elapsed.time > phase2_end_time_d16 & d16$elapsed.time <= phase3_end_time_d16,"shared.emotion"] == "interested"))

number.of.emotion.per.phase$interested <- number.of.emotion.per.phase$interested + interested
```

## focused
```{r}
phase1_end_time_d16 <- elapsed_time_d16 * (2/5)
phase2_end_time_d16 <- phase1_end_time_d16 * 2
phase3_end_time_d16 <- elapsed_time_d16

focused <- c(sum(d16[d16$elapsed.time <= phase1_end_time_d16,"shared.emotion"] == "focused"),
sum(d16[d16$elapsed.time > phase1_end_time_d16 & d16$elapsed.time <= phase2_end_time_d16 ,"shared.emotion"] == "focused"),
sum(d16[d16$elapsed.time > phase2_end_time_d16 & d16$elapsed.time <= phase3_end_time_d16,"shared.emotion"] == "focused"))

number.of.emotion.per.phase$focused <- number.of.emotion.per.phase$focused + focused 
```

## delighted
```{r}
phase1_end_time_d16 <- elapsed_time_d16 * (2/5)
phase2_end_time_d16 <- phase1_end_time_d16 * 2
phase3_end_time_d16 <- elapsed_time_d16

delighted <- c(sum(d16[d16$elapsed.time <= phase1_end_time_d16,"shared.emotion"] == "delighted"),
sum(d16[d16$elapsed.time > phase1_end_time_d16 & d16$elapsed.time <= phase2_end_time_d16 ,"shared.emotion"] == "delighted"),
sum(d16[d16$elapsed.time > phase2_end_time_d16 & d16$elapsed.time <= phase3_end_time_d16,"shared.emotion"] == "delighted"))

number.of.emotion.per.phase$delighted <- number.of.emotion.per.phase$delighted + delighted 
```

## satisfied
```{r}
phase1_end_time_d16 <- elapsed_time_d16 * (2/5)
phase2_end_time_d16 <- phase1_end_time_d16 * 2
phase3_end_time_d16 <- elapsed_time_d16

satisfied <- c(sum(d16[d16$elapsed.time <= phase1_end_time_d16,"shared.emotion"] == "satisfied"),
sum(d16[d16$elapsed.time > phase1_end_time_d16 & d16$elapsed.time <= phase2_end_time_d16 ,"shared.emotion"] == "satisfied"),
sum(d16[d16$elapsed.time > phase2_end_time_d16 & d16$elapsed.time <= phase3_end_time_d16,"shared.emotion"] == "satisfied"))

number.of.emotion.per.phase$satisfied <- number.of.emotion.per.phase$satisfied + satisfied 
```

## amused
```{r}
phase1_end_time_d16 <- elapsed_time_d16 * (2/5)
phase2_end_time_d16 <- phase1_end_time_d16 * 2
phase3_end_time_d16 <- elapsed_time_d16

amused <- c(sum(d16[d16$elapsed.time <= phase1_end_time_d16,"shared.emotion"] == "amused"),
sum(d16[d16$elapsed.time > phase1_end_time_d16 & d16$elapsed.time <= phase2_end_time_d16 ,"shared.emotion"] == "amused"),
sum(d16[d16$elapsed.time > phase2_end_time_d16 & d16$elapsed.time <= phase3_end_time_d16,"shared.emotion"] == "amused"))

number.of.emotion.per.phase$amused <- number.of.emotion.per.phase$amused + amused 
```

## relaxed
```{r}
phase1_end_time_d16 <- elapsed_time_d16 * (2/5)
phase2_end_time_d16 <- phase1_end_time_d16 * 2
phase3_end_time_d16 <- elapsed_time_d16

relaxed <- c(sum(d16[d16$elapsed.time <= phase1_end_time_d16,"shared.emotion"] == "relaxed"),
sum(d16[d16$elapsed.time > phase1_end_time_d16 & d16$elapsed.time <= phase2_end_time_d16 ,"shared.emotion"] == "relaxed"),
sum(d16[d16$elapsed.time > phase2_end_time_d16 & d16$elapsed.time <= phase3_end_time_d16,"shared.emotion"] == "relaxed"))

number.of.emotion.per.phase$relaxed <- number.of.emotion.per.phase$relaxed + relaxed 
```

# d21

```{r}
d21 <- data_eat[data_eat$dyad == "D21",]

elapsed_time_d21 <- sum(d21$duration)
```
## interested
```{r}
phase1_end_time_d21 <- elapsed_time_d21 * (2/5)
phase2_end_time_d21 <- phase1_end_time_d21 * 2
phase3_end_time_d21 <- elapsed_time_d21

interested <- c(sum(d21[d21$elapsed.time <= phase1_end_time_d21,"shared.emotion"] == "interested"),
sum(d21[d21$elapsed.time > phase1_end_time_d21 & d21$elapsed.time <= phase2_end_time_d21 ,"shared.emotion"] == "interested"),
sum(d21[d21$elapsed.time > phase2_end_time_d21 & d21$elapsed.time <= phase3_end_time_d21,"shared.emotion"] == "interested"))

number.of.emotion.per.phase$interested <- number.of.emotion.per.phase$interested + interested
```

## focused
```{r}
phase1_end_time_d21 <- elapsed_time_d21 * (2/5)
phase2_end_time_d21 <- phase1_end_time_d21 * 2
phase3_end_time_d21 <- elapsed_time_d21

focused <- c(sum(d21[d21$elapsed.time <= phase1_end_time_d21,"shared.emotion"] == "focused"),
sum(d21[d21$elapsed.time > phase1_end_time_d21 & d21$elapsed.time <= phase2_end_time_d21 ,"shared.emotion"] == "focused"),
sum(d21[d21$elapsed.time > phase2_end_time_d21 & d21$elapsed.time <= phase3_end_time_d21,"shared.emotion"] == "focused"))

number.of.emotion.per.phase$focused <- number.of.emotion.per.phase$focused + focused 
```

## delighted
```{r}
phase1_end_time_d21 <- elapsed_time_d21 * (2/5)
phase2_end_time_d21 <- phase1_end_time_d21 * 2
phase3_end_time_d21 <- elapsed_time_d21

delighted <- c(sum(d21[d21$elapsed.time <= phase1_end_time_d21,"shared.emotion"] == "delighted"),
sum(d21[d21$elapsed.time > phase1_end_time_d21 & d21$elapsed.time <= phase2_end_time_d21 ,"shared.emotion"] == "delighted"),
sum(d21[d21$elapsed.time > phase2_end_time_d21 & d21$elapsed.time <= phase3_end_time_d21,"shared.emotion"] == "delighted"))

number.of.emotion.per.phase$delighted <- number.of.emotion.per.phase$delighted + delighted 
```

## satisfied
```{r}
phase1_end_time_d21 <- elapsed_time_d21 * (2/5)
phase2_end_time_d21 <- phase1_end_time_d21 * 2
phase3_end_time_d21 <- elapsed_time_d21

satisfied <- c(sum(d21[d21$elapsed.time <= phase1_end_time_d21,"shared.emotion"] == "satisfied"),
sum(d21[d21$elapsed.time > phase1_end_time_d21 & d21$elapsed.time <= phase2_end_time_d21 ,"shared.emotion"] == "satisfied"),
sum(d21[d21$elapsed.time > phase2_end_time_d21 & d21$elapsed.time <= phase3_end_time_d21,"shared.emotion"] == "satisfied"))

number.of.emotion.per.phase$satisfied <- number.of.emotion.per.phase$satisfied + satisfied 
```

## amused
```{r}
phase1_end_time_d21 <- elapsed_time_d21 * (2/5)
phase2_end_time_d21 <- phase1_end_time_d21 * 2
phase3_end_time_d21 <- elapsed_time_d21

amused <- c(sum(d21[d21$elapsed.time <= phase1_end_time_d21,"shared.emotion"] == "amused"),
sum(d21[d21$elapsed.time > phase1_end_time_d21 & d21$elapsed.time <= phase2_end_time_d21 ,"shared.emotion"] == "amused"),
sum(d21[d21$elapsed.time > phase2_end_time_d21 & d21$elapsed.time <= phase3_end_time_d21,"shared.emotion"] == "amused"))

number.of.emotion.per.phase$amused <- number.of.emotion.per.phase$amused + amused 
```

## relaxed
```{r}
phase1_end_time_d21 <- elapsed_time_d21 * (2/5)
phase2_end_time_d21 <- phase1_end_time_d21 * 2
phase3_end_time_d21 <- elapsed_time_d21

relaxed <- c(sum(d21[d21$elapsed.time <= phase1_end_time_d21,"shared.emotion"] == "relaxed"),
sum(d21[d21$elapsed.time > phase1_end_time_d21 & d21$elapsed.time <= phase2_end_time_d21 ,"shared.emotion"] == "relaxed"),
sum(d21[d21$elapsed.time > phase2_end_time_d21 & d21$elapsed.time <= phase3_end_time_d21,"shared.emotion"] == "relaxed"))

number.of.emotion.per.phase$relaxed <- number.of.emotion.per.phase$relaxed + relaxed 
```

# d23

```{r}
d23 <- data_eat[data_eat$dyad == "D23",]

elapsed_time_d23 <- sum(d23$duration)
```
## interested
```{r}
phase1_end_time_d23 <- elapsed_time_d23 * (2/5)
phase2_end_time_d23 <- phase1_end_time_d23 * 2
phase3_end_time_d23 <- elapsed_time_d23

interested <- c(sum(d23[d23$elapsed.time <= phase1_end_time_d23,"shared.emotion"] == "interested"),
sum(d23[d23$elapsed.time > phase1_end_time_d23 & d23$elapsed.time <= phase2_end_time_d23 ,"shared.emotion"] == "interested"),
sum(d23[d23$elapsed.time > phase2_end_time_d23 & d23$elapsed.time <= phase3_end_time_d23,"shared.emotion"] == "interested"))

number.of.emotion.per.phase$interested <- number.of.emotion.per.phase$interested + interested
```

## focused
```{r}
phase1_end_time_d23 <- elapsed_time_d23 * (2/5)
phase2_end_time_d23 <- phase1_end_time_d23 * 2
phase3_end_time_d23 <- elapsed_time_d23

focused <- c(sum(d23[d23$elapsed.time <= phase1_end_time_d23,"shared.emotion"] == "focused"),
sum(d23[d23$elapsed.time > phase1_end_time_d23 & d23$elapsed.time <= phase2_end_time_d23 ,"shared.emotion"] == "focused"),
sum(d23[d23$elapsed.time > phase2_end_time_d23 & d23$elapsed.time <= phase3_end_time_d23,"shared.emotion"] == "focused"))

number.of.emotion.per.phase$focused <- number.of.emotion.per.phase$focused + focused 
```

## delighted
```{r}
phase1_end_time_d23 <- elapsed_time_d23 * (2/5)
phase2_end_time_d23 <- phase1_end_time_d23 * 2
phase3_end_time_d23 <- elapsed_time_d23

delighted <- c(sum(d23[d23$elapsed.time <= phase1_end_time_d23,"shared.emotion"] == "delighted"),
sum(d23[d23$elapsed.time > phase1_end_time_d23 & d23$elapsed.time <= phase2_end_time_d23 ,"shared.emotion"] == "delighted"),
sum(d23[d23$elapsed.time > phase2_end_time_d23 & d23$elapsed.time <= phase3_end_time_d23,"shared.emotion"] == "delighted"))

number.of.emotion.per.phase$delighted <- number.of.emotion.per.phase$delighted + delighted 
```

## satisfied
```{r}
phase1_end_time_d23 <- elapsed_time_d23 * (2/5)
phase2_end_time_d23 <- phase1_end_time_d23 * 2
phase3_end_time_d23 <- elapsed_time_d23

satisfied <- c(sum(d23[d23$elapsed.time <= phase1_end_time_d23,"shared.emotion"] == "satisfied"),
sum(d23[d23$elapsed.time > phase1_end_time_d23 & d23$elapsed.time <= phase2_end_time_d23 ,"shared.emotion"] == "satisfied"),
sum(d23[d23$elapsed.time > phase2_end_time_d23 & d23$elapsed.time <= phase3_end_time_d23,"shared.emotion"] == "satisfied"))

number.of.emotion.per.phase$satisfied <- number.of.emotion.per.phase$satisfied + satisfied 
```

## amused
```{r}
phase1_end_time_d23 <- elapsed_time_d23 * (2/5)
phase2_end_time_d23 <- phase1_end_time_d23 * 2
phase3_end_time_d23 <- elapsed_time_d23

amused <- c(sum(d23[d23$elapsed.time <= phase1_end_time_d23,"shared.emotion"] == "amused"),
sum(d23[d23$elapsed.time > phase1_end_time_d23 & d23$elapsed.time <= phase2_end_time_d23 ,"shared.emotion"] == "amused"),
sum(d23[d23$elapsed.time > phase2_end_time_d23 & d23$elapsed.time <= phase3_end_time_d23,"shared.emotion"] == "amused"))

number.of.emotion.per.phase$amused <- number.of.emotion.per.phase$amused + amused 
```

## relaxed
```{r}
phase1_end_time_d23 <- elapsed_time_d23 * (2/5)
phase2_end_time_d23 <- phase1_end_time_d23 * 2
phase3_end_time_d23 <- elapsed_time_d23

relaxed <- c(sum(d23[d23$elapsed.time <= phase1_end_time_d23,"shared.emotion"] == "relaxed"),
sum(d23[d23$elapsed.time > phase1_end_time_d23 & d23$elapsed.time <= phase2_end_time_d23 ,"shared.emotion"] == "relaxed"),
sum(d23[d23$elapsed.time > phase2_end_time_d23 & d23$elapsed.time <= phase3_end_time_d23,"shared.emotion"] == "relaxed"))

number.of.emotion.per.phase$relaxed <- number.of.emotion.per.phase$relaxed + relaxed 
```

# d26

```{r}
d26 <- data_eat[data_eat$dyad == "D26",]

elapsed_time_d26 <- sum(d26$duration)
```
## interested
```{r}
phase1_end_time_d26 <- elapsed_time_d26 * (2/5)
phase2_end_time_d26 <- phase1_end_time_d26 * 2
phase3_end_time_d26 <- elapsed_time_d26

interested <- c(sum(d26[d26$elapsed.time <= phase1_end_time_d26,"shared.emotion"] == "interested"),
sum(d26[d26$elapsed.time > phase1_end_time_d26 & d26$elapsed.time <= phase2_end_time_d26 ,"shared.emotion"] == "interested"),
sum(d26[d26$elapsed.time > phase2_end_time_d26 & d26$elapsed.time <= phase3_end_time_d26,"shared.emotion"] == "interested"))

number.of.emotion.per.phase$interested <- number.of.emotion.per.phase$interested + interested
```

## focused
```{r}
phase1_end_time_d26 <- elapsed_time_d26 * (2/5)
phase2_end_time_d26 <- phase1_end_time_d26 * 2
phase3_end_time_d26 <- elapsed_time_d26

focused <- c(sum(d26[d26$elapsed.time <= phase1_end_time_d26,"shared.emotion"] == "focused"),
sum(d26[d26$elapsed.time > phase1_end_time_d26 & d26$elapsed.time <= phase2_end_time_d26 ,"shared.emotion"] == "focused"),
sum(d26[d26$elapsed.time > phase2_end_time_d26 & d26$elapsed.time <= phase3_end_time_d26,"shared.emotion"] == "focused"))

number.of.emotion.per.phase$focused <- number.of.emotion.per.phase$focused + focused 
```

## delighted
```{r}
phase1_end_time_d26 <- elapsed_time_d26 * (2/5)
phase2_end_time_d26 <- phase1_end_time_d26 * 2
phase3_end_time_d26 <- elapsed_time_d26

delighted <- c(sum(d26[d26$elapsed.time <= phase1_end_time_d26,"shared.emotion"] == "delighted"),
sum(d26[d26$elapsed.time > phase1_end_time_d26 & d26$elapsed.time <= phase2_end_time_d26 ,"shared.emotion"] == "delighted"),
sum(d26[d26$elapsed.time > phase2_end_time_d26 & d26$elapsed.time <= phase3_end_time_d26,"shared.emotion"] == "delighted"))

number.of.emotion.per.phase$delighted <- number.of.emotion.per.phase$delighted + delighted 
```

## satisfied
```{r}
phase1_end_time_d26 <- elapsed_time_d26 * (2/5)
phase2_end_time_d26 <- phase1_end_time_d26 * 2
phase3_end_time_d26 <- elapsed_time_d26

satisfied <- c(sum(d26[d26$elapsed.time <= phase1_end_time_d26,"shared.emotion"] == "satisfied"),
sum(d26[d26$elapsed.time > phase1_end_time_d26 & d26$elapsed.time <= phase2_end_time_d26 ,"shared.emotion"] == "satisfied"),
sum(d26[d26$elapsed.time > phase2_end_time_d26 & d26$elapsed.time <= phase3_end_time_d26,"shared.emotion"] == "satisfied"))

number.of.emotion.per.phase$satisfied <- number.of.emotion.per.phase$satisfied + satisfied 
```

## amused
```{r}
phase1_end_time_d26 <- elapsed_time_d26 * (2/5)
phase2_end_time_d26 <- phase1_end_time_d26 * 2
phase3_end_time_d26 <- elapsed_time_d26

amused <- c(sum(d26[d26$elapsed.time <= phase1_end_time_d26,"shared.emotion"] == "amused"),
sum(d26[d26$elapsed.time > phase1_end_time_d26 & d26$elapsed.time <= phase2_end_time_d26 ,"shared.emotion"] == "amused"),
sum(d26[d26$elapsed.time > phase2_end_time_d26 & d26$elapsed.time <= phase3_end_time_d26,"shared.emotion"] == "amused"))

number.of.emotion.per.phase$amused <- number.of.emotion.per.phase$amused + amused 
```

## relaxed
```{r}
phase1_end_time_d26 <- elapsed_time_d26 * (2/5)
phase2_end_time_d26 <- phase1_end_time_d26 * 2
phase3_end_time_d26 <- elapsed_time_d26

relaxed <- c(sum(d26[d26$elapsed.time <= phase1_end_time_d26,"shared.emotion"] == "relaxed"),
sum(d26[d26$elapsed.time > phase1_end_time_d26 & d26$elapsed.time <= phase2_end_time_d26 ,"shared.emotion"] == "relaxed"),
sum(d26[d26$elapsed.time > phase2_end_time_d26 & d26$elapsed.time <= phase3_end_time_d26,"shared.emotion"] == "relaxed"))

number.of.emotion.per.phase$relaxed <- number.of.emotion.per.phase$relaxed + relaxed 
```

# d27

```{r}
d27 <- data_eat[data_eat$dyad == "D27",]

elapsed_time_d27 <- sum(d27$duration)
```
## interested
```{r}
phase1_end_time_d27 <- elapsed_time_d27 * (2/5)
phase2_end_time_d27 <- phase1_end_time_d27 * 2
phase3_end_time_d27 <- elapsed_time_d27

interested <- c(sum(d27[d27$elapsed.time <= phase1_end_time_d27,"shared.emotion"] == "interested"),
sum(d27[d27$elapsed.time > phase1_end_time_d27 & d27$elapsed.time <= phase2_end_time_d27 ,"shared.emotion"] == "interested"),
sum(d27[d27$elapsed.time > phase2_end_time_d27 & d27$elapsed.time <= phase3_end_time_d27,"shared.emotion"] == "interested"))

number.of.emotion.per.phase$interested <- number.of.emotion.per.phase$interested + interested
```

## focused
```{r}
phase1_end_time_d27 <- elapsed_time_d27 * (2/5)
phase2_end_time_d27 <- phase1_end_time_d27 * 2
phase3_end_time_d27 <- elapsed_time_d27

focused <- c(sum(d27[d27$elapsed.time <= phase1_end_time_d27,"shared.emotion"] == "focused"),
sum(d27[d27$elapsed.time > phase1_end_time_d27 & d27$elapsed.time <= phase2_end_time_d27 ,"shared.emotion"] == "focused"),
sum(d27[d27$elapsed.time > phase2_end_time_d27 & d27$elapsed.time <= phase3_end_time_d27,"shared.emotion"] == "focused"))

number.of.emotion.per.phase$focused <- number.of.emotion.per.phase$focused + focused 
```

## delighted
```{r}
phase1_end_time_d27 <- elapsed_time_d27 * (2/5)
phase2_end_time_d27 <- phase1_end_time_d27 * 2
phase3_end_time_d27 <- elapsed_time_d27

delighted <- c(sum(d27[d27$elapsed.time <= phase1_end_time_d27,"shared.emotion"] == "delighted"),
sum(d27[d27$elapsed.time > phase1_end_time_d27 & d27$elapsed.time <= phase2_end_time_d27 ,"shared.emotion"] == "delighted"),
sum(d27[d27$elapsed.time > phase2_end_time_d27 & d27$elapsed.time <= phase3_end_time_d27,"shared.emotion"] == "delighted"))

number.of.emotion.per.phase$delighted <- number.of.emotion.per.phase$delighted + delighted 
```

## satisfied
```{r}
phase1_end_time_d27 <- elapsed_time_d27 * (2/5)
phase2_end_time_d27 <- phase1_end_time_d27 * 2
phase3_end_time_d27 <- elapsed_time_d27

satisfied <- c(sum(d27[d27$elapsed.time <= phase1_end_time_d27,"shared.emotion"] == "satisfied"),
sum(d27[d27$elapsed.time > phase1_end_time_d27 & d27$elapsed.time <= phase2_end_time_d27 ,"shared.emotion"] == "satisfied"),
sum(d27[d27$elapsed.time > phase2_end_time_d27 & d27$elapsed.time <= phase3_end_time_d27,"shared.emotion"] == "satisfied"))

number.of.emotion.per.phase$satisfied <- number.of.emotion.per.phase$satisfied + satisfied 
```

## amused
```{r}
phase1_end_time_d27 <- elapsed_time_d27 * (2/5)
phase2_end_time_d27 <- phase1_end_time_d27 * 2
phase3_end_time_d27 <- elapsed_time_d27

amused <- c(sum(d27[d27$elapsed.time <= phase1_end_time_d27,"shared.emotion"] == "amused"),
sum(d27[d27$elapsed.time > phase1_end_time_d27 & d27$elapsed.time <= phase2_end_time_d27 ,"shared.emotion"] == "amused"),
sum(d27[d27$elapsed.time > phase2_end_time_d27 & d27$elapsed.time <= phase3_end_time_d27,"shared.emotion"] == "amused"))

number.of.emotion.per.phase$amused <- number.of.emotion.per.phase$amused + amused 
```

## relaxed
```{r}
phase1_end_time_d27 <- elapsed_time_d27 * (2/5)
phase2_end_time_d27 <- phase1_end_time_d27 * 2
phase3_end_time_d27 <- elapsed_time_d27

relaxed <- c(sum(d27[d27$elapsed.time <= phase1_end_time_d27,"shared.emotion"] == "relaxed"),
sum(d27[d27$elapsed.time > phase1_end_time_d27 & d27$elapsed.time <= phase2_end_time_d27 ,"shared.emotion"] == "relaxed"),
sum(d27[d27$elapsed.time > phase2_end_time_d27 & d27$elapsed.time <= phase3_end_time_d27,"shared.emotion"] == "relaxed"))

number.of.emotion.per.phase$relaxed <- number.of.emotion.per.phase$relaxed + relaxed 
```

# d29

```{r}
d29 <- data_eat[data_eat$dyad == "D29",]

elapsed_time_d29 <- sum(d29$duration)
```
## interested
```{r}
phase1_end_time_d29 <- elapsed_time_d29 * (2/5)
phase2_end_time_d29 <- phase1_end_time_d29 * 2
phase3_end_time_d29 <- elapsed_time_d29

interested <- c(sum(d29[d29$elapsed.time <= phase1_end_time_d29,"shared.emotion"] == "interested"),
sum(d29[d29$elapsed.time > phase1_end_time_d29 & d29$elapsed.time <= phase2_end_time_d29 ,"shared.emotion"] == "interested"),
sum(d29[d29$elapsed.time > phase2_end_time_d29 & d29$elapsed.time <= phase3_end_time_d29,"shared.emotion"] == "interested"))

number.of.emotion.per.phase$interested <- number.of.emotion.per.phase$interested + interested
```

## focused
```{r}
phase1_end_time_d29 <- elapsed_time_d29 * (2/5)
phase2_end_time_d29 <- phase1_end_time_d29 * 2
phase3_end_time_d29 <- elapsed_time_d29

focused <- c(sum(d29[d29$elapsed.time <= phase1_end_time_d29,"shared.emotion"] == "focused"),
sum(d29[d29$elapsed.time > phase1_end_time_d29 & d29$elapsed.time <= phase2_end_time_d29 ,"shared.emotion"] == "focused"),
sum(d29[d29$elapsed.time > phase2_end_time_d29 & d29$elapsed.time <= phase3_end_time_d29,"shared.emotion"] == "focused"))

number.of.emotion.per.phase$focused <- number.of.emotion.per.phase$focused + focused 
```

## delighted
```{r}
phase1_end_time_d29 <- elapsed_time_d29 * (2/5)
phase2_end_time_d29 <- phase1_end_time_d29 * 2
phase3_end_time_d29 <- elapsed_time_d29

delighted <- c(sum(d29[d29$elapsed.time <= phase1_end_time_d29,"shared.emotion"] == "delighted"),
sum(d29[d29$elapsed.time > phase1_end_time_d29 & d29$elapsed.time <= phase2_end_time_d29 ,"shared.emotion"] == "delighted"),
sum(d29[d29$elapsed.time > phase2_end_time_d29 & d29$elapsed.time <= phase3_end_time_d29,"shared.emotion"] == "delighted"))

number.of.emotion.per.phase$delighted <- number.of.emotion.per.phase$delighted + delighted 
```

## satisfied
```{r}
phase1_end_time_d29 <- elapsed_time_d29 * (2/5)
phase2_end_time_d29 <- phase1_end_time_d29 * 2
phase3_end_time_d29 <- elapsed_time_d29

satisfied <- c(sum(d29[d29$elapsed.time <= phase1_end_time_d29,"shared.emotion"] == "satisfied"),
sum(d29[d29$elapsed.time > phase1_end_time_d29 & d29$elapsed.time <= phase2_end_time_d29 ,"shared.emotion"] == "satisfied"),
sum(d29[d29$elapsed.time > phase2_end_time_d29 & d29$elapsed.time <= phase3_end_time_d29,"shared.emotion"] == "satisfied"))

number.of.emotion.per.phase$satisfied <- number.of.emotion.per.phase$satisfied + satisfied 
```

## amused
```{r}
phase1_end_time_d29 <- elapsed_time_d29 * (2/5)
phase2_end_time_d29 <- phase1_end_time_d29 * 2
phase3_end_time_d29 <- elapsed_time_d29

amused <- c(sum(d29[d29$elapsed.time <= phase1_end_time_d29,"shared.emotion"] == "amused"),
sum(d29[d29$elapsed.time > phase1_end_time_d29 & d29$elapsed.time <= phase2_end_time_d29 ,"shared.emotion"] == "amused"),
sum(d29[d29$elapsed.time > phase2_end_time_d29 & d29$elapsed.time <= phase3_end_time_d29,"shared.emotion"] == "amused"))

number.of.emotion.per.phase$amused <- number.of.emotion.per.phase$amused + amused 
```

## relaxed
```{r}
phase1_end_time_d29 <- elapsed_time_d29 * (2/5)
phase2_end_time_d29 <- phase1_end_time_d29 * 2
phase3_end_time_d29 <- elapsed_time_d29

relaxed <- c(sum(d29[d29$elapsed.time <= phase1_end_time_d29,"shared.emotion"] == "relaxed"),
sum(d29[d29$elapsed.time > phase1_end_time_d29 & d29$elapsed.time <= phase2_end_time_d29 ,"shared.emotion"] == "relaxed"),
sum(d29[d29$elapsed.time > phase2_end_time_d29 & d29$elapsed.time <= phase3_end_time_d29,"shared.emotion"] == "relaxed"))

number.of.emotion.per.phase$relaxed <- number.of.emotion.per.phase$relaxed + relaxed 
```
```{r}
number.of.emotion.per.phase
```
